Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-09-22 analy_eval.tex
[review] 1. Radii in fig. 6 indicated. 2. Typo fixed and definition added for the Hurwitz calculation 3. Redundant equations removed and reference to them added 4. Fig 7-10, the legend for error bar modified. (a) and (b) added

\begin{figure}[htb]
\centering
\includegraphics[width=\columnwidth]{fig_H-tau_fold}
\caption{Left: Diagram of Loschmidt echo that reduces to a partition function, where time is the horizontal direction, the dashed (solid) lines are open (gluing) boundary conditions. Red arrows are the directions of Hamiltonian flow that propagates the dashed line boundary state to the solid line boundary state. The blue semi-circles are the UV regulators and they are identified as periodic boundaries in the direction perpendicular to the red arrow (equal time slice). Middle: Image of the map $\xi = \frac{z}{\tau - z}$. Right: Image of $w = \ln \xi$. It is a cylinder by identifying the blue lines and the standard radial quantization procedure can be applied. }
\label{fig:H-tau_fold}
\end{figure}

@@

For the process ($c$ is assumed to be the same as $a$)
\begin{equation}
S_i( \theta_1 ) \rightarrow S_j( \theta_2 ) ,
\end{equation}
the free energy is
\begin{equation}
\mathcal{F}( \beta )  = 
\left\lbrace
\begin{aligned}
  &\frac{1}{2}(|x| - x^2 )\beta  \quad &i = j \\
  &\frac{1}{16}\beta   \quad &i \ne j ,  \\
\end{aligned} \right. \quad x = \frac{\theta_2 - \theta_1}{\pi} .
\end{equation}
We can then read off the fidelity and Loschmidt echo power law decay exponent with the identification $\beta = 2 \ln L$ and $ 4 \ln \tau$.

As analyzed in Sec.~\ref{sec:analytic_numerics}, $S_2( \theta)$ interpolates between DD and NN, $S_1( \theta )$ interpolates between DN and ND. In the region accessible to the numerical calculation in the lattice model, we choose the process 
\begin{equation}
\label{eq:DDDD}
{\rm DD} + {\rm DD} \rightarrow  \lambda + {\rm DD},
\end{equation}
to verify
\begin{equation}
\label{eq:result_DDDD}
\mathcal{F} = 
\left\lbrace
\begin{aligned}
\frac{1}{8}\ln L  &\quad\text{fidelity}  \\
\frac{1}{4}\ln t   &\quad \text{echo} .  \\
\end{aligned} \right.  
\end{equation}
The same results have already been obtained for $\lambda = {\rm P}$\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}. Another process
\begin{equation}
\label{eq:DNDN}
{\rm DN} + {\rm DN} \rightarrow \lambda + {\rm DN} ,
\end{equation}
is used to verify
\begin{equation}
\label{eq:result_DNDN}
\mathcal{F} = 
\left\lbrace
\begin{aligned}
 (x - x^2 )\ln L   &  \quad {\rm fidelity} \\
 2(x - x^2 ) \ln t  & \quad \text{ Loschmidt echo} , \\
\end{aligned} \right. 
\end{equation}
where $\lambda = \tan \theta$ and $x = \frac{\theta}{\pi}$.

>>>>

\begin{figure}[htb]
\centering
\includegraphics[width=\columnwidth]{fig_H-tau_fold}
\caption{Left: Diagram of Loschmidt echo that reduces to a partition function, where time is the horizontal direction, the dashed (solid) lines are open (gluing) boundary conditions. Red arrows are the directions of Hamiltonian flow that propagates the dashed line boundary state to the solid line boundary state. The blue semi-circles {\color{red} of radii $\epsilon$} are the UV regulators and they are identified as periodic boundaries in the direction perpendicular to the red arrow (equal time slice). Middle: Image of the map $\xi = \frac{z}{\tau - z}$. {\color{red}The two semi-circles have radii $({\tau}/{\epsilon})^{\pm1}$ respectively.}  Right: Image of $w = \ln \xi$. It is a cylinder by identifying the blue lines and the standard radial quantization procedure can be applied. }
\label{fig:H-tau_fold}
\end{figure}

@@

For the process ($c$ is assumed to be the same as $a$)
\begin{equation}
\label{eq:S_i_S_j}
S_i( \theta_1 ) \rightarrow S_j( \theta_2 ) ,
\end{equation}
the free energy is
\begin{equation}
\mathcal{F}( \beta )  = 
\left\lbrace
\begin{aligned}
  &\frac{1}{2}(|x| - x^2 )\beta  \quad &i = j \\
  &\frac{1}{16}\beta   \quad &i \ne j ,  \\
\end{aligned} \right. \quad x = \frac{\theta_2 - \theta_1}{\pi} .
\end{equation}
We can then read off the fidelity and Loschmidt echo power law decay exponent with the identification $\beta = 2 \ln L$ and $ 4 \ln \tau$.

As analyzed in Sec.~\ref{sec:analytic_numerics}, $S_2( \theta)$ interpolates between DD and NN, $S_1( \theta )$ interpolates between DN and ND. In the region accessible to the numerical calculation in the lattice model, we choose the process 
\begin{equation}
\label{eq:DDDD}
{\rm DD} + {\rm DD} \rightarrow  \lambda + {\rm DD},
\end{equation}
to verify
\begin{equation}
\label{eq:result_DDDD}
\mathcal{F} = 
\left\lbrace
\begin{aligned}
\frac{1}{8}\ln L  &\quad\text{fidelity}  \\
\frac{1}{4}\ln t   &\quad \text{echo} .  \\
\end{aligned} \right.  
\end{equation}
The same results have already been obtained for $\lambda = {\rm P}$\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}. Another process {\color{red} in Eq.~\eqref{eq:DNDN}}
%\begin{equation}
%\label{eq:DNDN}
%{\rm DN} + {\rm DN} \rightarrow \lambda + {\rm DN} ,
%\end{equation}
is used to verify
\begin{equation}
\label{eq:result_DNDN}
\mathcal{F} = 
\left\lbrace
\begin{aligned}
 (x - x^2 )\ln L   &  \quad {\rm fidelity} \\
 2(x - x^2 ) \ln t  & \quad \text{ Loschmidt echo} , \\
\end{aligned} \right. 
\end{equation}
where $\lambda = \tan \theta$ and $x = \frac{\theta}{\pi}$.

### 2017-09-22 conclusion.tex
[draft] wording changes for descritive text.
[review] 1. Radii in fig. 6 indicated. 2. Typo fixed and definition added for the Hurwitz calculation 3. Redundant equations removed and reference to them added 4. Fig 7-10, the legend for error bar modified. (a) and (b) added

We began by classifying the boundary states by two types of $S$ matrices $S_1(\theta)$ and $S_2(\theta)$, where the parameter $\theta$ -- the scattering angle -- is determined by the transmission coefficient of the interface. The conventional `DD', `NN' boundary conditions belong to special choice of $\theta$ in $S_1$ and  `DN' and P belongs to $S_2$. Generic value of $\theta$ then interpolates those conventional boundary conditions. A harmonic chain model allows us to realize part of these partially-transmitive boundary conditions in a concrete lattice setting.

The dynamical behavior of the Loschmidt echo reflects the change of the conformal interface, which we denote as
\begin{equation}
S_i( \theta_1 ) \rightarrow S_j( \theta_2 ) 
\end{equation}
Its power law decay exponent is related to the scaling dimension of the bcc operator that mediates these interfaces. Analytic computation shows that the exponent is always $\frac{1}{4}$ when the change of boundary condition is made between different types of $S$ matrices ($i \ne j$), regardless of the choice of $\theta$. On the other hand, the exponent depends on the difference of angles $\theta_1 - \theta_2$ as a quadratic relation when the change is made between the same types of $S$ matrices ($i = j$).

>>>>

We began by classifying the boundary states by two types of $S$ matrices $S_1(\theta)$ and $S_2(\theta)$, where the parameter $\theta$ -- the scattering angle -- is determined by the transmission coefficient of the interface. The conventional `DD', `NN' boundary conditions belong to special choice of $\theta$ in $S_1$ and  `DN' and P belongs to $S_2$. Generic value of $\theta$ then interpolates between those conventional boundary conditions. A harmonic chain model allows us to realize part of these partially-transmitive boundary conditions in a concrete lattice setting.

The dynamical behavior of the Loschmidt echo reflects the change of the conformal interface during the process described in {\color{red}Eq.~\eqref{eq:S_i_S_j}}.
%, which we denote as
%\begin{equation}
%S_i( \theta_1 ) \rightarrow S_j( \theta_2 )  \quad i, j = 1, 2. 
%\end{equation}
Its power law decay exponent is related to the scaling dimension of the bcc operator that mediates these interfaces. Analytic computation shows that the exponent is always $\frac{1}{4}$ when the change of boundary condition is made between different types of $S$ matrices ($i \ne j$), regardless of the choice of $\theta$. On the other hand, the exponent depends on the difference of angles $\theta_1 - \theta_2$ as a quadratic relation when the change is made between the same types of $S$ matrices ($i = j$).

### 2017-09-22 disc.tex
[review] 1. Radii in fig. 6 indicated. 2. Typo fixed and definition added for the Hurwitz calculation 3. Redundant equations removed and reference to them added 4. Fig 7-10, the legend for error bar modified. (a) and (b) added

% analytic results type 1 -> type 2, c/4; 
In the Sec.~\ref{sec_sub:analy_eval}, we have presented the analytic results for the general process (assuming the far end boundary condition $c$ is the same as prior-quench interface $a$) 
\begin{equation}
 S_i( \theta_1 ) \rightarrow S_j( \theta_2 ),
\end{equation}
We find that if the conformal interfaces are of different types, i.e. $i \ne j$, the (long time) free energy is always $\frac{1}{4} \ln t$, regardless of the theta angles. The two types of conformal interface do not talk to each other because they impose on different fields. If we treat $S_1$ as a combination of Dirichlet and Neumann boundary conditions imposed on the rotated $\phi$ fields as in Eq.~\eqref{eq:rotation_a_basis}, then $S_2$ imposes one of them on the duel field of $\phi$. In the derivation of the $M$ matrix, these two correspond to the parts of the Lorentz group and can not be connected even by taking singular value of $\lambda$. It is then reasonable to find an universal echo between them. The special value of ${\rm DD} \rightarrow P$ also agrees with the existing general CFT result of completely transparent interface\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}.

@@

For the more interesting case where the boundary condition are of the same type, we have verified the quadratic angle dependence numerically for this process 
\begin{equation}
{\rm DN} + {\rm DN} \rightarrow \lambda + {\rm DN} . 
\end{equation}
The process gives a series of new bcc operator dimensions of the $c = 2$ boson boundary CFT. Our numerical curve of the Loschmidt echo is not as perfect as the fidelity calculation (where smaller shift regulator can be used). Such discrepancy is very likely due to the existence of the free boson zero mode, as moving away from massless point remedies the situation. The special case of ${\rm DN} \rightarrow {\rm P}$ agrees with the Ref.~\onlinecite{kennes_universal_2014,stephan_logarithmic_2013}, where the difference of this exponent $\frac{3}{8}$ and the ${\rm DD} \rightarrow {\rm P}$ one of $\frac{1}{4}$ is interpreted as twice the dimension of bcc operator dimension ($\frac{1}{16}$) that transforms D to N. This picture is complete in this full ${\rm DN}$ to $\lambda $ transition, where other possible primary fields fuse DN into $\lambda$. In a rational boson theory, the number of primary fields is finite. It requires further study to identify these bcc operators and explore their physical significance.

Our numerical study also shows that the far end boundary condition $c$, which in the large system size limit should not impact the system, {\it does change} the scaling dimension in a way that is not captured by our analytic computation. The reason is that the boundary condition on the far end may introduce additional bcc operators and thus change the free energy. It would be interesting to have a CFT calculation that reproduces the better numerical result of
\begin{equation}
{\rm DN} + {\rm P} \rightarrow \lambda + {\rm P} 
\end{equation}
shown in Fig.~\ref{fig:PDN_fit}.

>>>>

% analytic results type 1 -> type 2, c/4; 
In the Sec.~\ref{sec_sub:analy_eval}, we have presented the analytic results for the general process {\color{red}described in Eq.~\eqref{eq:S_i_S_j}} (assuming the far end boundary condition $c$ is the same as prior-quench interface $a$).
%\begin{equation}
% S_i( \theta_1 ) \rightarrow S_j( \theta_2 ),
%\end{equation}
We find that if the conformal interfaces are of different types, i.e. $i \ne j$, the (long time) free energy is always $\frac{1}{4} \ln t$, regardless of the theta angles. The two types of conformal interface do not talk to each other because they impose on different fields. If we treat $S_1$ as a combination of Dirichlet and Neumann boundary conditions imposed on the rotated $\phi$ fields as in Eq.~\eqref{eq:rotation_a_basis}, then $S_2$ imposes one of them on the duel field of $\phi$. In the derivation of the $M$ matrix, these two correspond to the parts of the Lorentz group and can not be connected even by taking singular value of $\lambda$. It is then reasonable to find an universal echo between them. The special value of ${\rm DD} \rightarrow P$ also agrees with the existing general CFT result of completely transparent interface\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}.

@@

For the more interesting case where the boundary condition are of the same type, we have verified the quadratic angle dependence numerically for {\color{red}the process in Eq.~\eqref{eq:DNDN}.}
%this process 
%\begin{equation}
%{\rm DN} + {\rm DN} \rightarrow \lambda + {\rm DN} . 
%\end{equation}
The process gives a series of new bcc operator dimensions of the $c = 2$ boson boundary CFT. Our numerical curve of the Loschmidt echo is not as perfect as the fidelity calculation (where smaller shift regulator can be used). Such discrepancy is very likely due to the existence of the free boson zero mode, as moving away from massless point remedies the situation. The special case of ${\rm DN} \rightarrow {\rm P}$ agrees with the Ref.~\onlinecite{kennes_universal_2014,stephan_logarithmic_2013}, where the difference of this exponent $\frac{3}{8}$ and the ${\rm DD} \rightarrow {\rm P}$ one of $\frac{1}{4}$ is interpreted as twice the dimension of bcc operator dimension ($\frac{1}{16}$) that transforms D to N. This picture is complete in this full ${\rm DN}$ to $\lambda $ transition, where other possible primary fields fuse DN into $\lambda$. In a rational boson theory, the number of primary fields is finite. It requires further study to identify these bcc operators and explore their physical significance.

Our numerical study also shows that the far end boundary condition $c$, which in the large system size limit should not impact the system, {\it does change} the scaling dimension in a way that is not captured by our analytic computation. The reason is that the boundary condition on the far end may introduce additional bcc operators and thus change the free energy. It would be interesting to have a CFT calculation that reproduces the better numerical result {\color{red}for the process in Eq.~\eqref{eq:DNP_rand()}, as}
%of
%\begin{equation}
%{\rm DN} + {\rm P} \rightarrow \lambda + {\rm P} 
%\end{equation}
shown in Fig.~\ref{fig:PDN_fit}.

### 2017-09-22 num_result.tex
[review] 1. Radii in fig. 6 indicated. 2. Typo fixed and definition added for the Hurwitz calculation 3. Redundant equations removed and reference to them added 4. Fig 7-10, the legend for error bar modified. (a) and (b) added

\begin{figure}[h]
\includegraphics[width=1\columnwidth]{DDDD_fit.pdf}
\caption{The Loschmidt echo decay exponent of the process $\text{DD}+\text{DD}\rightarrow\lambda+\text{DD}$, with gluing condition $S_1(\theta)$. We work with the total system size $N = 30000$ sites, and parameters $m = 10^{-8}$, $k = 1$. The lattice constant is set to unity. The blue dots representing the numerical results lie on the red analytic line. As predicted, the echo exponents are all equal for different values of $\theta$. Inset: An example of Loschmidt echo with $\theta = 0.02 \pi$ shown in log-log scale. The dashline denotes the expected power law of $t^{-0.25}$. Finite size effect does not emerge before $t=10^{3}$, which sets the right boundary of the range we fit. See main text for the curve fitting method.}
\label{fig:DDDD}
\end{figure}

@@

We start with the process
\begin{equation}
\text{DD}+\text{DD}\rightarrow\lambda+\text{DD},
\end{equation}
and show its Loschmidt echo in Fig.~\ref{fig:DDDD}. The inset is a typical Loschmidt echo diagram, whose linear decreasing behavior in the log-log axes indicates the expected power law decay. We also provide the analytic prediction $\mathcal{L}(t)\sim t^{-0.25}$ (\cf Eq.~\eqref{eq:result_DDDD}) as contrast. The exponent (negative of the slope of the line in log-log plot) is calculated by fitting such diagrams for $\theta = 0.01n \pi$, $n = 1,...,50 $. The fitting is performed before the finite size revival surges and error is estimated by assuming independent and identical Gaussian distribution for each point. We see that the exponents all match with the $\frac{1}{4}$ theoretical line within error.

@@

Next we analyze the more interesting $\theta$ dependent process
\begin{equation}
  \text{DN}+\text{DN}\rightarrow\lambda+\text{DN},
\end{equation}
in which the joining boundary condition is determined by $S_1(\theta)$. A direct calculation with the mass regulator do not perform very well in the small $\theta$ regime: The exponent is slightly larger than the theoretical prediction. We therefore turn to another regulator that shift the far end boundary condition DN to $S_1( \delta \theta )$ and consider the following process
\begin{eqnarray}\begin{aligned}
\label{eq:approx_DNDN}
S_1(0)+S_1(\delta\theta)\rightarrow S_1(\theta)+S_1(\delta\theta),
\end{aligned}\end{eqnarray}
Since ${\rm DN} = S_1 (0 )$, taking smaller and smaller $\delta \theta$ should correspond to the original process. This ``shift" regulator works very well for the fidelity calculation, where $\delta \theta = 0.001 \pi$, while moderately good for the Loschmidt echo, where $\delta \theta = 0.003\pi$, see Fig.~\ref{fig:DDNN}. The inset shows the $\theta$-dependence of power law decay, and the corresponding exponents follows the quadratic relation as predicted in Eq.~\eqref{eq:result_DNDN}. We leave further discussion of introducing $\delta\theta$ in Sec.~\ref{sec:disc}.

\begin{figure}
  \centering
\includegraphics[width=1\columnwidth]{DDNN_fit.pdf}
\includegraphics[width=1\columnwidth]{DDNN_fidel_fit.pdf}
    \caption{The slope of the free energy for Loschmidt echo (a) and bipartite fidelity (b) in the process $\text{DN}+\text{DN}\rightarrow\lambda+\text{DN}$. The total system size is $N=35000$ sites with the same parameters as in Fig.~\ref{fig:DDDD}. The numerical value of exponents follow a quadratic relation as predicted. There is still visible deviation from the analytic results in (a) due to the subtlety of zero mode, see the discussion in the main text. Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.12\pi $ and $0.24\pi$. Finite size effect does not emerge before $t=10^{4}$. We use the same curve fitting method as described for Fig.~\ref{fig:DDDD}.}
      \label{fig:DDNN}
\end{figure}

We finally consider the case
\begin{equation}
\text{P}+\text{P}\rightarrow\lambda+\text{P},
\end{equation}
in Fig.~\ref{fig:PPPP}. Since ${\rm P} = S_1( \frac{\pi}{4} ) $, the zero mode now occurs at $\theta = \frac{\pi}{4}$. We therefore apply the shift regulator there 
\begin{equation}
\begin{aligned}
\label{eq:approx_DNDN}
S_2\left(\frac{\pi}{4}\right)+S_2\left(\frac{\pi}{4}+\delta\theta\right)\rightarrow S_2(\theta)+S_2\left(\frac{\pi}{4}+\delta\theta\right),
\end{aligned}
\end{equation}
where we take $\delta\theta=0.003\pi$. The $\theta$ dependent exponents now are symmetric about $\theta=\frac{\pi}{4}$ and quadratic on each side, in accordance to Eq.~\eqref{eq:periodic-case}.

\begin{figure}
  \centering
  \includegraphics[width=1\columnwidth]{PP_fit.pdf}
    \includegraphics[width=1\columnwidth]{PP_fidel_fit.pdf}
    \caption{The decay exponent of Loschmidt echo (a) and bipartite fidelity (b) for process $\text{P}+\text{P}\rightarrow\lambda+\text{P}$. The parameters are the same as those in Fig.~\ref{fig:DDNN}. The plot is symmetric with respect to $\theta=0.25\pi$ as predicted. The deviation around $\frac{\pi}{4}$ in (a) is small but visible, see the discussion in the main text. Inset in (a): From top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.04\pi, 0.08\pi $ and $0.18\pi$. Finite size effect does not emerge before $t=10^{4}$. We use the same curve fitting method as described for Fig.~\ref{fig:DDDD}.}
    \label{fig:PPPP}
\end{figure}

Finally, we also provide the data for the process
\begin{equation}
{\rm DN} + {\rm P} \rightarrow \lambda  + {\rm P},
\end{equation}
to evaluate the influence of the boundary condition $c$. It {\rm does} influence the scaling dimension, which is not captured by our analytic calculation. Specifically, the large value of $\theta$ still follows the quadratic relation with a deficit of $\frac{1}{8}$, while the small $\theta$ value has smaller deficit and merge with the analytic curve at $\theta = 0$. 
\begin{figure}[htb]
\centering
\includegraphics[width=1\columnwidth]{PDN_fit.pdf}
\caption{The decay exponent of Loschmidt echo in the process ${\rm DN} + {\rm P} \rightarrow \lambda  + {\rm P}$. The boundary condition $c$, which is now different from $a$, changes the scaling completely from the analytic quadratic curve. The deficit to the analytic value is roughly $\frac{1}{8}$ for $\theta > \frac{\pi}{4}$, It becomes smaller and approaches zero for small $\theta$. }
\label{fig:PDN_fit}
\end{figure}

>>>>

\begin{figure}[h]
\includegraphics[width=1\columnwidth]{DDDD_fit.pdf}
\caption{The Loschmidt echo decay exponent of the process in {\color{red}Eq.~\eqref{eq:DDDD}}, with gluing condition $S_1(\theta)$. We work with the total system size $N = 30000$ sites, and parameters $m = 10^{-8}$, $k = 1$. The lattice constant is set to unity. The blue dots representing the numerical results lie on the red analytic line. As predicted, the echo exponents are all equal for different values of $\theta$. Inset: An example of Loschmidt echo with $\theta = 0.02 \pi$ shown in log-log scale. The dashline denotes the expected power law of $t^{-0.25}$. Finite size effect does not emerge before $t=10^{3}$, which sets the right boundary of the range we fit. See main text for the curve fitting method.}
\label{fig:DDDD}
\end{figure}

@@

We start with the process in {\color{red}Eq.~\eqref{eq:DDDD}}, 
%\begin{equation}
%\text{DD}+\text{DD}\rightarrow\lambda+\text{DD},
%\end{equation}
and show its Loschmidt echo in Fig.~\ref{fig:DDDD}. The inset is a typical Loschmidt echo diagram, whose linear decreasing behavior in the log-log axes indicates the expected power law decay. We also provide the analytic prediction $\mathcal{L}(t)\sim t^{-0.25}$ (\cf Eq.~\eqref{eq:result_DDDD}) as contrast. The exponent (negative of the slope of the line in log-log plot) is calculated by fitting such diagrams for $\theta = 0.01n \pi$, $n = 1,...,50 $. The fitting is performed before the finite size revival surges and error is estimated by assuming independent and identical Gaussian distribution for each point. We see that the exponents all match with the $\frac{1}{4}$ theoretical line within error.

@@

Next we analyze the more interesting $\theta$ dependent process {\color{red}described in Eq.~\eqref{eq:DNDN},}
%\begin{equation}
%  \text{DN}+\text{DN}\rightarrow\lambda+\text{DN},
%\end{equation}
in which the joining boundary condition is determined by $S_1(\theta)$. A direct calculation with the mass regulator do not perform very well in the small $\theta$ regime: The exponent is slightly larger than the theoretical prediction. We therefore turn to another regulator that shift the far end boundary condition DN to $S_1( \delta \theta )$ and consider the following process
\begin{eqnarray}\begin{aligned}
\label{eq:approx_DNDN}
S_1(0)+S_1(\delta\theta)\rightarrow S_1(\theta)+S_1(\delta\theta),
\end{aligned}\end{eqnarray}
Since ${\rm DN} = S_1 (0 )$, taking smaller and smaller $\delta \theta$ should correspond to the original process. This ``shift" regulator works very well for the fidelity calculation, where $\delta \theta = 0.001 \pi$, while moderately good for the Loschmidt echo, where $\delta \theta = 0.003\pi$, see Fig.~\ref{fig:DDNN}. The inset shows the $\theta$-dependence of power law decay, and the corresponding exponents follows the quadratic relation as predicted in Eq.~\eqref{eq:result_DNDN}. We leave further discussion of introducing $\delta\theta$ in Sec.~\ref{sec:disc}.

\begin{figure}
  \centering
\includegraphics[width=1\columnwidth]{DDNN_fit.pdf}
\includegraphics[width=1\columnwidth]{DDNN_fidel_fit.pdf}
    \caption{The slope of the free energy for Loschmidt echo (a) and bipartite fidelity (b) {\color{red}for the process in Eq.~\eqref{eq:DNDN}.}The total system size is $N=35000$ sites with the same parameters as in Fig.~\ref{fig:DDDD}. The numerical value of exponents follow a quadratic relation as predicted. There is still visible deviation from the analytic results in (a) due to the subtlety of zero mode, see the discussion in the main text. Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.12\pi $ and $0.24\pi$. Finite size effect does not emerge before $t=10^{4}$. We use the same curve fitting method as described for Fig.~\ref{fig:DDDD}.}
      \label{fig:DDNN}
\end{figure}

We finally consider the {\color{red}process in Eq.~\eqref{eq:PP}}
%\begin{equation}
%\text{P}+\text{P}\rightarrow\lambda+\text{P},
%\end{equation}
in Fig.~\ref{fig:PPPP}. Since ${\rm P} = S_1( \frac{\pi}{4} ) $, the zero mode now occurs at $\theta = \frac{\pi}{4}$. We therefore apply the shift regulator there 
\begin{equation}
\begin{aligned}
\label{eq:approx_DNDN}
S_2\left(\frac{\pi}{4}\right)+S_2\left(\frac{\pi}{4}+\delta\theta\right)\rightarrow S_2(\theta)+S_2\left(\frac{\pi}{4}+\delta\theta\right),
\end{aligned}
\end{equation}
where we take $\delta\theta=0.003\pi$. The $\theta$ dependent exponents now are symmetric about $\theta=\frac{\pi}{4}$ and quadratic on each side, in accordance to Eq.~\eqref{eq:periodic-case}.

\begin{figure}
  \centering
  \includegraphics[width=1\columnwidth]{PP_fit.pdf}
    \includegraphics[width=1\columnwidth]{PP_fidel_fit.pdf}
    \caption{The decay exponent of Loschmidt echo (a) and bipartite fidelity (b) for the process {\color{red}in Eq.~\eqref{eq:PP}}. The parameters are the same as those in Fig.~\ref{fig:DDNN}. The plot is symmetric with respect to $\theta=0.25\pi$ as predicted. The deviation around $\frac{\pi}{4}$ in (a) is small but visible, see the discussion in the main text. Inset in (a): From top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.04\pi, 0.08\pi $ and $0.18\pi$. Finite size effect does not emerge before $t=10^{4}$. We use the same curve fitting method as described for Fig.~\ref{fig:DDDD}.}
    \label{fig:PPPP}
\end{figure}

Finally, we also provide the data for the process
\begin{equation}
\label{eq:DNP_rand()}
{\rm DN} + {\rm P} \rightarrow \lambda  + {\rm P},
\end{equation}
to evaluate the influence of the boundary condition $c$. It {\rm does} influence the scaling dimension, which is not captured by our analytic calculation. Specifically, the large value of $\theta$ still follows the quadratic relation with a deficit of $\frac{1}{8}$, while the small $\theta$ value has smaller deficit and merge with the analytic curve at $\theta = 0$. 
\begin{figure}[htb]
\centering
\includegraphics[width=1\columnwidth]{PDN_fit.pdf}
\caption{The decay exponent of Loschmidt echo for the process {\color{red}in Eq.~\eqref{eq:DNP_rand()}.} The boundary condition $c$, which is now different from $a$, changes the scaling completely from the analytic quadratic curve. The deficit to the analytic value is roughly $\frac{1}{8}$ for $\theta > \frac{\pi}{4}$, It becomes smaller and approaches zero for small $\theta$. }
\label{fig:PDN_fit}
\end{figure}
